Technique for \earlywarning\ filtering for compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-29 inspiral_svd.tex
Removed 'The' from first sentence of abstract: 'Rapid detection of compact binary coalescence...'
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1178 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for
multi-messenger astronomy.  Prompt detection alerts to the astronomical
community may make it possible to observe the onset of electromagnetic emission
from compact binary coalescence.  We demonstrate a computationally practical
filtering strategy that could produce early-warning triggers before
gravitational radiation from the final merger has arrived at the detectors.
\end{abstract}

>>>>

\begin{abstract}
Rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for
multi-messenger astronomy.  Prompt detection alerts to the astronomical
community may make it possible to observe the onset of electromagnetic emission
from compact binary coalescence.  We demonstrate a computationally practical
filtering strategy that could produce early-warning triggers before
gravitational radiation from the final merger has arrived at the detectors.
\end{abstract}
